---
title: "MPN Geocoding Notebook"
author: "Sara Patino"
date: "Published on `r format(Sys.time(), '%m-%d-%y')`"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 5
    page-layout: full
    embed-resources: true
fig-cap-location: top
editor:
  markdown:
    wrap: 72
execute: 
  echo: false
  output: true
---

:::{.callout-note}
df_files was saved to box in folder `DIR Provided MPN Plans` with file name `mpn_summary_data`
:::


```{r}
library(stringr)
library(tidyverse)
library(merced.clc)
library(readxl)
library(dplyr)
```

Listing all the folders, recursive shows empty subfolder name
```{r}
list.dirs(path = here::here("data"), 
          full.names = FALSE,
          recursive = TRUE)

```

Tracking down empty subfolder name
```{r}

for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfolder = list.dirs(path = x, 
          full.names = FALSE,
          recursive = FALSE)


  if(length(subfolder) > 0) {print(x)}
  
}

```

```{r}
x= here::here("data/MPN 0060/")

subfolder = list.dirs(path = x, 
          full.names = FALSE,
          recursive = FALSE)

if(length(subfolder) > 0) {print(x)}
```

Listing files within mpn 0060 folder
```{r}
list.files(path = here::here("data/MPN 0060"))
```

run a for loop through the folders to pull all files and put into one character vector (df_files).
```{r}
df_files = c()
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = list.files(path = x, 
          full.names = FALSE,
          recursive = FALSE)
  df_files = c(df_files, subfiles)
  
}

```

Detect files with 'geo'- (lower case 'g' was not working); and create a character vector with these files
```{r}
df_files = str_to_lower(df_files, locale = "en")
str_detect(df_files, "geo")
str_count(df_files, pattern = "geo")
geocoding_files <- str_subset(df_files, pattern = "geo", negate = FALSE)
```


create table describing folders
```{r}
df_files = tribble(~folder, 
                   ~num_geo_files,
                   ~num_pdf_files,
                   ~num_excel_files)
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = str_to_lower(list.files(path = x,
                                     full.names = FALSE,
                                     recursive = FALSE),
                          locale = "en")
  num_geo = sum(str_detect(subfiles, "geo"))
  
  num_pdf = sum(str_detect(subfiles,"pdf"))
  
  num_excel = sum(str_detect(subfiles, "xlsx|xls"))
  
  df_files = df_files %>%
    add_row(folder = basename(x),
            num_geo_files = num_geo,
            num_pdf_files = num_pdf,
            num_excel_files = num_excel)
  
}

```

do some folders have xlsx and xls?
```{r}
df_files = tribble(~folder, 
                   ~num_geo_files,
                   ~num_pdf_files,
                   ~num_excel_files,
                   ~list_geo_files,
                   ~all_excel_files,
                   ~all_pdf_files)
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = str_to_lower(list.files(path = x,
                                     full.names = FALSE,
                                     recursive = FALSE),
                          locale = "en")
  num_geo = sum(str_detect(subfiles, "geo"))
  
  geo_files = paste(str_subset(subfiles, 
                         pattern = "geo", 
                         negate = FALSE),
                    collapse = "; ")
  
  num_pdf = sum(str_detect(subfiles,"pdf"))
  
  num_excel = sum(str_detect(subfiles, "xlsx|xls"))
  
  excel_files = paste(str_subset(subfiles,
                                 pattern = "xlsx|xls",
                                 negate = FALSE),
                      collapse = ";")
  pdf_files = paste(str_subset(subfiles,
                               pattern = "pdf",
                               negate = FALSE),
                    collapse = ";")
  
  
  df_files = df_files %>%
    add_row(folder = basename(x),
            num_geo_files = num_geo,
            num_pdf_files = num_pdf,
            num_excel_files = num_excel,
            list_geo_files = geo_files,
            all_excel_files = excel_files,
            all_pdf_files = pdf_files)
  
}

```

```{r}
#| eval: false
df_files %>% 
  write_csv(x=.,
            file = here::here("reference/mpn_meta_data.csv"))

```


# geocode file cleaning
Going to load in a few geo code files to see if they have commonalities that we can write general code from

## mpn0060
Contains sheets for PTP, HospitalER, Specialties zip codes met
```{r}
zipmet_sheets <- readxl::excel_sheets(here::here("data/MPN 0060/Attachment C - Geocode.xlsx")) %>%  
  as_tibble() %>%  
  filter(!str_detect(string = value, 
                    pattern = "NotMet|Zip|ZIPS"))

```

```{r}
df_sheets = c()
for (i in zipmet_sheets$value) {
 
  
  this_list = readxl::read_excel(path = here::here("data/MPN 0060/Attachment C - Geocode.xlsx"),
                                 sheet = i,
                                 col_names = str_to_lower(i))
  
  df_sheets = c(df_sheets, this_list)
}    

```
  

## mpn0079
This file contains a sheet labeled "access standards not met"

```{r}
zipmet_sheets2 <- readxl::excel_sheets(here::here("data/MPN 0079/CompWest Select MPN 0079 Geocoding Exhibit.xlsx")) %>%  
  as_tibble() %>%  
  filter(!str_detect(string = value, 
                    pattern = "All MPN Zip Codes|Access"))

```

```{r}
df_sheets2 = c()
for(i in zipmet_sheets2$value) {
  
  this_list = readxl::read_excel(path = here::here("data/MPN 0079/CompWest Select MPN 0079 Geocoding Exhibit.xlsx"),
                                 sheet = i,
                                 col_names = str_to_lower(i),
                                 col_types = c("numeric", "blank", "blank", "blank"),
                                 skip = 2)
  
  df_sheets2 = c(df_sheets2, this_list)
}

```



find alternate plans? "Access Standards" "Exhibit F" ; leave exhibit F last 
create code that gets the correct excel file with data and input new column with the geo file we will work with 


files that are geo and xlsx files; # of pdfs that arent data; create a column- each row contains list of name of geo files