---
title: "MPN Geocoding Notebook"
author: "Sara Patino"
date: "Published on `r format(Sys.time(), '%m-%d-%y')`"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 5
    page-layout: full
    embed-resources: true
fig-cap-location: top
editor:
  markdown:
    wrap: 72
execute: 
  echo: false
  output: true
---

:::{.callout-note}
df_files was saved to box in folder `DIR Provided MPN Plans` with file name `mpn_summary_data`
:::


```{r}
library(stringr)
library(tidyverse)
library(merced.clc)
library(readxl)
library(dplyr)
```

Listing all the folders, recursive shows empty subfolder name
```{r}
list.dirs(path = here::here("data"), 
          full.names = FALSE,
          recursive = TRUE)

```

Tracking down empty subfolder name
```{r}

for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfolder = list.dirs(path = x, 
          full.names = FALSE,
          recursive = FALSE)


  if(length(subfolder) > 0) {print(x)}
  
}

```

```{r}
x= here::here("data/MPN 0060/")

subfolder = list.dirs(path = x, 
          full.names = FALSE,
          recursive = FALSE)

if(length(subfolder) > 0) {print(x)}
```

Listing files within mpn 0060 folder
```{r}
list.files(path = here::here("data/MPN 0060"))
```

run a for loop through the folders to pull all files and put into one character vector (df_files).
```{r}
df_files = c()
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = list.files(path = x, 
          full.names = FALSE,
          recursive = FALSE)
  df_files = c(df_files, subfiles)
  
}

```

Detect files with 'geo'- (lower case 'g' was not working); and create a character vector with these files
```{r}
df_files = str_to_lower(df_files, locale = "en")
str_detect(df_files, "geo")
str_count(df_files, pattern = "geo")
geocoding_files <- str_subset(df_files, pattern = "geo", negate = FALSE)
```


create table describing folders
```{r}
df_files = tribble(~folder, 
                   ~num_geo_files,
                   ~num_pdf_files,
                   ~num_excel_files)
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = str_to_lower(list.files(path = x,
                                     full.names = FALSE,
                                     recursive = FALSE),
                          locale = "en")
  num_geo = sum(str_detect(subfiles, "geo"))
  
  num_pdf = sum(str_detect(subfiles,"pdf"))
  
  num_excel = sum(str_detect(subfiles, "xlsx|xls"))
  
  df_files = df_files %>%
    add_row(folder = basename(x),
            num_geo_files = num_geo,
            num_pdf_files = num_pdf,
            num_excel_files = num_excel)
  
}

```

do some folders have xlsx and xls?
```{r}
df_files = tribble(~folder, 
                   ~num_geo_files,
                   ~num_pdf_files,
                   ~num_excel_files,
                   ~list_geo_files,
                   ~all_excel_files,
                   ~all_pdf_files)
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = str_to_lower(list.files(path = x,
                                     full.names = FALSE,
                                     recursive = FALSE),
                          locale = "en")
  num_geo = sum(str_detect(subfiles, "geo"))
  
  geo_files = paste(str_subset(subfiles, 
                         pattern = "geo", 
                         negate = FALSE),
                    collapse = "; ")
  
  num_pdf = sum(str_detect(subfiles,"pdf"))
  
  num_excel = sum(str_detect(subfiles, "xlsx|xls"))
  
  excel_files = paste(str_subset(subfiles,
                                 pattern = "xlsx|xls",
                                 negate = FALSE),
                      collapse = ";")
  pdf_files = paste(str_subset(subfiles,
                               pattern = "pdf",
                               negate = FALSE),
                    collapse = ";")
  
  
  df_files = df_files %>%
    add_row(folder = basename(x),
            num_geo_files = num_geo,
            num_pdf_files = num_pdf,
            num_excel_files = num_excel,
            list_geo_files = geo_files,
            all_excel_files = excel_files,
            all_pdf_files = pdf_files)
  
}

```

```{r}
#| eval: false
df_files %>% 
  write_csv(x=.,
            file = here::here("reference/mpn_meta_data.csv"))

```


# geocode file cleaning
Going to load in a few geo code files to see if they have commonalities that we can write general code from

## mpn0060
Contains sheets for PTP, HospitalER, Specialties zip codes met
```{r}
zipmet_sheets <- readxl::excel_sheets(here::here("data/MPN 0060/Attachment C - Geocode.xlsx")) %>%  
  as_tibble() %>%  
  filter(!str_detect(string = value, 
                    pattern = "NotMet|Zip|ZIPS"))

```

```{r}
df_sheets = c()
for (i in zipmet_sheets$value) {
 
  
  this_list = readxl::read_excel(path = here::here("data/MPN 0060/Attachment C - Geocode.xlsx"),
                                 sheet = i,
                                 col_names = str_to_lower(i))
  
  df_sheets = c(df_sheets, this_list)
}    

```
  

## mpn0079
This file contains a sheet labeled "access standards not met"

```{r}
zipmet_sheets2 <- readxl::excel_sheets(here::here("data/MPN 0079/CompWest Select MPN 0079 Geocoding Exhibit.xlsx")) %>%  
  as_tibble() %>%  
  filter(!str_detect(string = value, 
                    pattern = "All MPN Zip Codes|Access"))

```

```{r}
df_sheets2 = c()
for(i in zipmet_sheets2$value) {
  
  this_list = readxl::read_excel(path = here::here("data/MPN 0079/CompWest Select MPN 0079 Geocoding Exhibit.xlsx"),
                                 sheet = i,
                                 col_names = str_to_lower(i),
                                 col_types = c("numeric", "blank", "blank", "blank"),
                                 skip = 2)
  
  df_sheets2 = c(df_sheets2, this_list)
}

```

:::{.callout-note}
The original meta data table was saved as `mpn_meta_data` and then Sara added to it manually and saved the 
edited file as `mpn_meta_data_manual.csv`. 
:::

```{r}
mpn_meta_data <- read_csv(here::here("reference/mpn_meta_data_manual.csv"))
View(mpn_meta_data)
```


# geocode file loading sheets
```{r}
this_mpn <- "MPN 0060"
this_geocode_file <- "Attachment C - Geocode.xlsx"


#loop over every mpn in mpn_meta_data table
for(i in this_mpn) {
  
  print(i) 
  
    #first get list of every tab in that mpns geo file   
  sheets_list = readxl::excel_sheets(path = paste0(here::here("data/"), 
                                                   this_mpn,
                                                   "/",
                                                   this_geocode_file))
  
  #create a for loop that loops through sheets list and loads each tab
  df_sheets = c()
  for (this_sheet in sheets_list) {
   
    
    this_list = readxl::read_excel(path = paste0(here::here("data/"), 
                                                   this_mpn,
                                                   "/",
                                                   this_geocode_file),
                                   sheet = this_sheet,
                                   col_names = this_sheet)
    
    df_sheets = c(df_sheets, this_list)
  }    

  
}
  


```


find alternate plans? "Access Standards" "Exhibit F" ; leave exhibit F last 
create code that gets the correct excel file with data and input new column with the geo file we will work with 

# Step 1 : Loading Attachment C - Geocode Files (most common filename)

```{r}
mpn_meta_data_manual %>% 
  count(geocode_file) %>% 
  arrange(desc(n)) %>% 
  merced.clc::dt_table(search = F,
                       row_nums = T)
```


#Step- 2: Pulling MPNs with "attachment c" (or most common) filenames

```{r}
attachment_c_filenames = mpn_meta_data_manual %>% 
  filter(str_detect(geocode_file,
                    pattern = regex("attachment c -",
                                    ignore_case = TRUE))) %>% 
  select(folder,
         geocode_file)

# create an empty list
```


#Step 3- For loop to extract all sheet names from "attachment c" (or other common filename) 

```{r}
identify_sheets = tibble(sheet = character(),
                         mpn = character())
for(mpn in seq(1,length(attachment_c_filenames$folder),1)) {
  
  print(attachment_c_filenames$folder[[mpn]])
                                                
  this_path = paste0(here::here("data/"), 
                attachment_c_filenames$folder[[mpn]],
                "/",
                attachment_c_filenames$geocode_file[[mpn]])    
  
  sheet_names = readxl::excel_sheets(path = this_path)
  
   identify_sheets = identify_sheets %>% 
    add_row(sheet = sheet_names,
            mpn = attachment_c_filenames$folder[[mpn]])
  
 #subset_sheets = paste(str_subset(identify_sheets,
                                 #pattern = "zip|not|zips"))
}
```

#Step 4- Identify "zipnotmet" sheet names for all files using the tibble created in step 3

```{r}
identify_sheets %>% 
  distinct(sheet)
```

#Step 5- Create a dataframe that will hold all "zipnotmet" sheet names after filtering through "identify_sheets"

```{r}
zipnotmet_sheet <- identify_sheets %>% 
  filter(str_detect(string = sheet,
                    pattern = "ZIPS|Zipsnotmet|Not Met Zips|Zips Not Met|C-5-ZipsNotmet|C5 - Not Met Zips|C5 Not Met Zips|ZipCodes Not Met|ZipCodesNotMet"))
```

#Step 6- Combine newly created tibble of "zipnotmet" sheets with existing dataframe (i.e. attachment_c_filenames)

```{r}
attachment_c_filenames = attachment_c_filenames %>% 
  left_join(zipnotmet_sheet, 
          by = c("folder" = "mpn"))

```


#Step 7- Now that we have folder, filename, and sheet name we use a for loop to extract the actual zips not met sheet data***
```{r}

sheet_data = list()
for(mpn in seq(1,length(attachment_c_filenames$folder),1)) {
  
  print(attachment_c_filenames$folder[[mpn]])
                                                
  this_path = paste0(here::here("data/"), 
                attachment_c_filenames$folder[[mpn]],
                "/",
                attachment_c_filenames$geocode_file[[mpn]])    
  
  #sheet_names = readxl::excel_sheets(path = this_path)
  
   
  zipnotmet_data = readxl::read_excel(path = this_path,
                                      sheet = attachment_c_filenames$sheet[[mpn]])
  #identify_sheets = identify_sheets %>% 
    #add_row(sheet = sheet_names,
           # mpn = attachment_c_filenames$folder[[mpn]])
  
  sheet_data[[mpn]] = zipnotmet_data
   #subset_sheets = paste(str_subset(identify_sheets,
                                 #pattern = "zip|not|zips"))

}

```

#Step 8- Identify the format that "zipnotmet" data is in (Type 1-6) using the mpn_meta_data_manual

#Step 9- Create a dataframe for each table format and loop through to pull the data in identical format
##Attachment- C, Table format 1
```{r}
table_format_1 <- attachment_c_filenames %>% 
  inner_join(., 
             y= mpn_meta_data_manual %>% 
                select(folder,
                type_of_table_format),
             by= "folder") %>% 
  filter(type_of_table_format == "Type 1: 3 col") 
```

##Attachment C- Type 1 Tables
```{r}
these_col_names <- c("ptp", "hospital_er", "specialties")


#loop over every mpn in mpn_meta_data table
df_sheets = list()
for(mpn in seq(1,length(table_format_1$folder),1)) {
  
  print(table_format_1$folder[[mpn]])
  #create a for loop that loops through sheets list and loads each tab
  
    this_path = paste0(here::here("data/"), 
                table_format_1$folder[[mpn]],
                "/",
                table_format_1$geocode_file[[mpn]])
    
   this_table = readxl::read_excel(path = this_path,
                                   sheet = table_format_1$sheet[[mpn]],
                                   col_names = these_col_names,
                                   skip = 1,
                                   col_types = "text") %>% 
     mutate(mpn = table_format_1$folder[[mpn]])
  
    
    df_sheets[[mpn]] = this_table
  }    

  
```

##Attachment C- Format 4
```{r}
table_format_4 <- attachment_c_filenames %>% 
  inner_join(., 
             y= mpn_meta_data_manual %>% 
                select(folder,
                type_of_table_format),
             by= "folder") %>% 
  filter(type_of_table_format == "Type 4: 7 col") 
```

```{r}
these_col_names_ <- c("zip_code", "ptp", "hospital_er", "orthopedist", "neurologist", "podiatrist", "chiropractor")


df_sheets2 = list()
for(mpn in seq(1,length(table_format_4$folder),1)) {
  
  print(table_format_4$folder[[mpn]])
  #create a for loop that loops through sheets list and loads each tab
  
    this_path = paste0(here::here("data/"), 
                table_format_4$folder[[mpn]],
                "/",
                table_format_4$geocode_file[[mpn]])
    
   this_table = readxl::read_excel(path = this_path,
                                   sheet = table_format_4$sheet[[mpn]],
                                   col_names = these_col_names_,
                                   skip = 2,
                                   col_types = "text") %>% 
     mutate(mpn = table_format_4$folder[[mpn]])
  
    
    df_sheets2[[mpn]] = this_table
  }    

  
```

##Attachment C- Table Format 3
```{r}
table_format_3 <- attachment_c_filenames %>% 
  inner_join(., 
             y= mpn_meta_data_manual %>% 
                select(folder,
                type_of_table_format),
             by= "folder") %>% 
  filter(type_of_table_format == "Type 3: 1 col (ZC)") 
```

```{r}
these_col_names_ <- c("zip_code")


df_sheets3 = list()
for(mpn in seq(1,length(table_format_3$folder),1)) {
  
  print(table_format_3$folder[[mpn]])
  #create a for loop that loops through sheets list and loads each tab
  
    this_path = paste0(here::here("data/"), 
                table_format_3$folder[[mpn]],
                "/",
                table_format_3$geocode_file[[mpn]])
    
   this_table = readxl::read_excel(path = this_path,
                                   sheet = table_format_3$sheet[[mpn]],
                                   col_names = these_col_names_,
                                   skip = 1,
                                   col_types = "text") %>% 
   mutate(mpn = table_format_3$folder[[mpn]])
  
    
    df_sheets3[[mpn]] = this_table
  }    
```


##Attachment C- Table Format 2
```{r}
table_format_2 <- attachment_c_filenames %>% 
  inner_join(., 
             y= mpn_meta_data_manual %>% 
                select(folder,
                type_of_table_format),
             by= "folder") %>% 
  filter(type_of_table_format == "Type 2: RF") 
```

```{r}
these_col_names_ <- c("zip_code", "ptp", "hospital_er", "occm", "ortho", "neuro", "nsg", "pm", "pmr", "psych", "psy", "gp", "im", "dpm", "dc", "lac")


df_sheets4 = list()
for(mpn in seq(1,length(table_format_2$folder),1)) {
  
  print(table_format_2$folder[[mpn]])
  #create a for loop that loops through sheets list and loads each tab
  
    this_path = paste0(here::here("data/"), 
                table_format_2$folder[[mpn]],
                "/",
                table_format_2$geocode_file[[mpn]])
    
   this_table = readxl::read_excel(path = this_path,
                                   sheet = table_format_2$sheet[[mpn]],
                                   col_names = these_col_names_,
                                   skip = 2,
                                   col_types = "text") %>% 
      mutate(mpn = table_format_2$folder[[mpn]])
  
    
    df_sheets4[[mpn]] = this_table
  }    
```

##Attachment C- Table Format 5
```{r}
table_format_5 <- attachment_c_filenames %>% 
  inner_join(., 
             y= mpn_meta_data_manual %>% 
                select(folder,
                type_of_table_format),
             by= "folder") %>% 
  filter(type_of_table_format == "Type 5: 4 col") 
```

```{r}
these_col_names_ <- c("zip code", "type", "15mi", "30mi")


df_sheets5 = list()
for(mpn in seq(1,length(table_format_5$folder),1)) {
  
  print(table_format_5$folder[[mpn]])
  #create a for loop that loops through sheets list and loads each tab
  
    this_path = paste0(here::here("data/"), 
                table_format_5$folder[[mpn]],
                "/",
                table_format_5$geocode_file[[mpn]])
    
   this_table = readxl::read_excel(path = this_path,
                                   sheet = table_format_5$sheet[[mpn]],
                                   col_names = these_col_names_,
                                   skip = 1)
  
    
    df_sheets5[[mpn]] = this_table
  }    
```

##Attachment C- Table Format 6
```{r}
table_format_6 <- attachment_c_filenames %>% 
  inner_join(., 
             y= mpn_meta_data_manual %>% 
                select(folder,
                type_of_table_format),
             by= "folder") %>% 
  filter(type_of_table_format == "Type 6: 2 col (w data)") 
```

```{r}
these_col_names_ <- c("zip_code", "zip_code2")


df_sheets6 = list()
for(mpn in seq(1,length(table_format_6$folder),1)) {
  
  print(table_format_6$folder[[mpn]])
  #create a for loop that loops through sheets list and loads each tab
  
    this_path = paste0(here::here("data/"), 
                table_format_6$folder[[mpn]],
                "/",
                table_format_6$geocode_file[[mpn]])
    
   this_table = readxl::read_excel(path = this_path,
                                   sheet = table_format_6$sheet[[mpn]],
                                   col_names = these_col_names_,
                                   skip = 1)
  
    
    df_sheets6[[mpn]] = this_table
  }    
```

```{r}
unique_zips = df_sheets %>% 
  bind_rows() %>% 
  pivot_longer(cols = c("ptp","hospital_er", "specialties"),
               names_to = "specialty",
               values_to = "zip_code") %>% 
  distinct(zip_code, mpn)

df_sheetscombine = df_sheets %>% 
  bind_rows()

df_sheets %>% 
  bind_rows() %>% 
  mutate(ptp = if_else(ptp %in% unique_zips$zip_code, "NM", NA),
         hospital_er = if_else(hospital_er %in% unique_zips$zip_code, "NM", NA),
         specialties = if_else(specialties %in% unique_zips$zip_code, "NM", NA)) %>% 
  View()

```

#Step 10- 

```{r}
all_dfsheets = tibble(zip_code = character(),
                      mpn = character(),
                      ptp = character(),
                      hospital_er = character(),
                      specialties = character())
for(df in df_sheets){
  unique_zips = df %>% 
  pivot_longer(cols = c("ptp","hospital_er", "specialties"),
               names_to = "specialty",
               values_to = "zip_code") %>% 
  distinct(zip_code, mpn) %>% 
    filter(!is.na(zip_code))
  
  this_df = unique_zips %>% 
    mutate(ptp = if_else(zip_code %in% df$ptp, "NM", NA),
         hospital_er = if_else(zip_code %in% df$hospital_er, "NM", NA),
         specialties = if_else(zip_code %in% df$specialties, "NM", NA))
 
  all_dfsheets = bind_rows(all_dfsheets, this_df) 
  
}

```

```{r}
all_dfsheets %>% 
  count(zip_code,
        mpn) %>% 
  arrange(desc(n))

```

#Combine format 1 and 4 and 2 (ptp hospital_er mpn zip code) 
```{r}
df_1_4_2 = bind_rows(all_dfsheets %>% 
  select(-specialties),

df_sheets2 %>% 
  bind_rows() %>% 
  select(zip_code, ptp, hospital_er, mpn),
df_sheets4 %>% 
  bind_rows() %>% 
  select(zip_code, ptp, hospital_er, mpn))


```

#2668 zip codes accross 59 mpns with 2 specialties

```{r}
df_1_4_2 %>% 
  summarize(num_mpn = n_distinct(mpn),
            num_zip = n_distinct(zip_code))
```

```{r}
write_csv(df_1_4_2, 
          here::here("reference/type1_4_2ptp_hospital.csv"))
```




#For any given zip code for a given column does the zip code exist within its mpn
#91901 could exist in mpn A 
#need to do this code chunk grouped by mpn using mutate
```{r}
unique_zips %>% 
  mutate(ptp = if_else(zip_code %in% df_sheetscombine$ptp, "NM", NA),
         hospital_er = if_else(zip_code %in% df_sheetscombine$hospital_er, "NM", NA),
         specialties = if_else(zip_code %in% df_sheetscombine$specialties, "NM", NA))

```


```{r}
df_sheets2 %>% 
  bind_rows()

```




#Sheet names
#ZIPSnotmet, Zipsnotmet, Not Met Zips, Zips Not Met, C-5-ZipsNotmet, C5 - Not Met Zips, C5 Not Met Zips, ZipCodes Not Met, ZipCodesNotMet
```{r}
df_identify %>% 
  count(identify_sheets) %>% 
  arrange(desc(n)) %>% 
  merced.clc::dt_table(search = F,
                       row_nums = T)
```





#other common words in geocode excel files (repeat attachment c process)





















