---
title: "MPN Geocoding Notebook"
author: "Sara Patino"
date: "Published on `r format(Sys.time(), '%m-%d-%y')`"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 5
    page-layout: full
    embed-resources: true
fig-cap-location: top
editor:
  markdown:
    wrap: 72
execute: 
  echo: false
  output: true
---

:::{.callout-note}
df_files was saved to box in folder `DIR Provided MPN Plans` with file name `mpn_summary_data`
:::


```{r}
library(stringr)
library(tidyverse)
library(merced.clc)
library(readxl)
library(dplyr)
```

Listing all the folders, recursive shows empty subfolder name
```{r}
list.dirs(path = here::here("data"), 
          full.names = FALSE,
          recursive = TRUE)

```

Tracking down empty subfolder name
```{r}

for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfolder = list.dirs(path = x, 
          full.names = FALSE,
          recursive = FALSE)


  if(length(subfolder) > 0) {print(x)}
  
}

```

```{r}
x= here::here("data/MPN 0060/")

subfolder = list.dirs(path = x, 
          full.names = FALSE,
          recursive = FALSE)

if(length(subfolder) > 0) {print(x)}
```

Listing files within mpn 0060 folder
```{r}
list.files(path = here::here("data/MPN 0060"))
```

run a for loop through the folders to pull all files and put into one character vector (df_files).
```{r}
df_files = c()
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = list.files(path = x, 
          full.names = FALSE,
          recursive = FALSE)
  df_files = c(df_files, subfiles)
  
}

```

Detect files with 'geo'- (lower case 'g' was not working); and create a character vector with these files
```{r}
df_files = str_to_lower(df_files, locale = "en")
str_detect(df_files, "geo")
str_count(df_files, pattern = "geo")
geocoding_files <- str_subset(df_files, pattern = "geo", negate = FALSE)
```


create table describing folders
```{r}
df_files = tribble(~folder, 
                   ~num_geo_files,
                   ~num_pdf_files,
                   ~num_excel_files)
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = str_to_lower(list.files(path = x,
                                     full.names = FALSE,
                                     recursive = FALSE),
                          locale = "en")
  num_geo = sum(str_detect(subfiles, "geo"))
  
  num_pdf = sum(str_detect(subfiles,"pdf"))
  
  num_excel = sum(str_detect(subfiles, "xlsx|xls"))
  
  df_files = df_files %>%
    add_row(folder = basename(x),
            num_geo_files = num_geo,
            num_pdf_files = num_pdf,
            num_excel_files = num_excel)
  
}

```

do some folders have xlsx and xls?
```{r}
df_files = tribble(~folder, 
                   ~num_geo_files,
                   ~num_pdf_files,
                   ~num_excel_files,
                   ~list_geo_files,
                   ~all_excel_files,
                   ~all_pdf_files)
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = str_to_lower(list.files(path = x,
                                     full.names = FALSE,
                                     recursive = FALSE),
                          locale = "en")
  num_geo = sum(str_detect(subfiles, "geo"))
  
  geo_files = paste(str_subset(subfiles, 
                         pattern = "geo", 
                         negate = FALSE),
                    collapse = "; ")
  
  num_pdf = sum(str_detect(subfiles,"pdf"))
  
  num_excel = sum(str_detect(subfiles, "xlsx|xls"))
  
  excel_files = paste(str_subset(subfiles,
                                 pattern = "xlsx|xls",
                                 negate = FALSE),
                      collapse = ";")
  pdf_files = paste(str_subset(subfiles,
                               pattern = "pdf",
                               negate = FALSE),
                    collapse = ";")
  
  
  df_files = df_files %>%
    add_row(folder = basename(x),
            num_geo_files = num_geo,
            num_pdf_files = num_pdf,
            num_excel_files = num_excel,
            list_geo_files = geo_files,
            all_excel_files = excel_files,
            all_pdf_files = pdf_files)
  
}

```

```{r}
#| eval: false
df_files %>% 
  write_csv(x=.,
            file = here::here("reference/mpn_meta_data.csv"))

```


# geocode file cleaning
Going to load in a few geo code files to see if they have commonalities that we can write general code from

## mpn0060
Contains sheets for PTP, HospitalER, Specialties zip codes met
```{r}
zipmet_sheets <- readxl::excel_sheets(here::here("data/MPN 0060/Attachment C - Geocode.xlsx")) %>%  
  as_tibble() %>%  
  filter(!str_detect(string = value, 
                    pattern = "NotMet|Zip|ZIPS"))

```

```{r}
df_sheets = c()
for (i in zipmet_sheets$value) {
 
  
  this_list = readxl::read_excel(path = here::here("data/MPN 0060/Attachment C - Geocode.xlsx"),
                                 sheet = i,
                                 col_names = str_to_lower(i))
  
  df_sheets = c(df_sheets, this_list)
}    

```
  

## mpn0079
This file contains a sheet labeled "access standards not met"

```{r}
zipmet_sheets2 <- readxl::excel_sheets(here::here("data/MPN 0079/CompWest Select MPN 0079 Geocoding Exhibit.xlsx")) %>%  
  as_tibble() %>%  
  filter(!str_detect(string = value, 
                    pattern = "All MPN Zip Codes|Access"))

```

```{r}
df_sheets2 = c()
for(i in zipmet_sheets2$value) {
  
  this_list = readxl::read_excel(path = here::here("data/MPN 0079/CompWest Select MPN 0079 Geocoding Exhibit.xlsx"),
                                 sheet = i,
                                 col_names = str_to_lower(i),
                                 col_types = c("numeric", "blank", "blank", "blank"),
                                 skip = 2)
  
  df_sheets2 = c(df_sheets2, this_list)
}

```

:::{.callout-note}
The original meta data table was saved as `mpn_meta_data` and then Sara added to it manually and saved the 
edited file as `mpn_meta_data_manual.csv`. 
:::

```{r}
mpn_meta_data <- read_csv(here::here("reference/mpn_meta_data_manual.csv"))
View(mpn_meta_data)
```


# geocode file loading sheets
```{r}
this_mpn <- "MPN 0060"
this_geocode_file <- "Attachment C - Geocode.xlsx"


#loop over every mpn in mpn_meta_data table
for(i in this_mpn) {
  
  print(i) 
  
    #first get list of every tab in that mpns geo file   
  sheets_list = readxl::excel_sheets(path = paste0(here::here("data/"), 
                                                   this_mpn,
                                                   "/",
                                                   this_geocode_file))
  
  #create a for loop that loops through sheets list and loads each tab
  df_sheets = c()
  for (this_sheet in sheets_list) {
   
    
    this_list = readxl::read_excel(path = paste0(here::here("data/"), 
                                                   this_mpn,
                                                   "/",
                                                   this_geocode_file),
                                   sheet = this_sheet,
                                   col_names = this_sheet)
    
    df_sheets = c(df_sheets, this_list)
  }    

  
}
  


```


find alternate plans? "Access Standards" "Exhibit F" ; leave exhibit F last 
create code that gets the correct excel file with data and input new column with the geo file we will work with 

# Loading Attachment C - Geocode Files

Looking for most common geocode_file names, so we can target the most common types first for data loading.
```{r}
mpn_meta_data %>% 
  count(geocode_file) %>% 
  arrange(desc(n)) %>% 
  merced.clc::dt_table(search = F,
                       row_nums = T)
```

We see that files beginning with the substring "Attachment C - geocode.xlsx" are most common, with 25 files having that exact filename. Additionally, there are 50 files that start with "Attachment C -" and have custom suffixes in their filenames. Combining these, we can just focus on all files beginning with "Attachment C -", and have a starting sample size of about 75 MPNs. 

The rough plan:

1. Create a loop that goes through all "Attachment C -" files. This will create a list of dataframes. These dataframes will pull in the `ZIPSnotmet` sheet from each file. And these dataframes will be in one long list. The name of each item/dataframe in the list will be the MPN name. 

2. Then we will look through the data for patterns in the column names and the number of columns. 

3. Then we'll create an empty dataframe that contains the full structure of the output table we hope to end with.

4. Then we'll write functions for mapping the individual dataframes in the list to the single output dataframe. For example, some sheets will include a "specialties" column, and some tables won't. Some will instead include "neurology" for example. We'll need to create an empty dataframe that has all of these possibilities. When an individual file only has "specialties" then the neuro, etc columns will be empty. Otherwise, the individual specialties will be filled in, and we will combine those to fill the overall "specialities" column. 


```{r}
attachment_c_filenames = mpn_meta_data %>% 
  filter(str_detect(geocode_file,
                    pattern = regex("attachment c -",
                                    ignore_case = TRUE))) %>% 
  select(folder,
         geocode_file)

# create an empty list
```

#For loop for extracting the zips not met data 
```{r}
#identify_sheets = tibble(sheet = character(),
                       #  mpn = character())
sheet_data = list()
for(mpn in seq(1,length(attachment_c_filenames$folder),1)) {
  
  print(attachment_c_filenames$folder[[mpn]])
                                                
  this_path = paste0(here::here("data/"), 
                attachment_c_filenames$folder[[mpn]],
                "/",
                attachment_c_filenames$geocode_file[[mpn]])    
  
  #sheet_names = readxl::excel_sheets(path = this_path)
  
   
  zipnotmet_data = readxl::read_excel(path = this_path,
                                      sheet = attachment_c_filenames$sheet[[mpn]])
  #identify_sheets = identify_sheets %>% 
    #add_row(sheet = sheet_names,
           # mpn = attachment_c_filenames$folder[[mpn]])
  
  sheet_data[[mpn]] = zipnotmet_data
   #subset_sheets = paste(str_subset(identify_sheets,
                                 #pattern = "zip|not|zips"))

}

```


```{r}
identify_sheets %>% 
  distinct(mpn)


```

#Creating new dataframe that includes zip not met sheet
```{r}
zipnotmet_sheet <- identify_sheets %>% 
  filter(str_detect(string = sheet,
                    pattern = "ZIPS|Zipsnotmet|Not Met Zips|Zips Not Met|C-5-ZipsNotmet|C5 - Not Met Zips|C5 Not Met Zips|ZipCodes Not Met|ZipCodesNotMet"))

#figure out expression for pattern parameter that gets all correct zipsnotmet sheet names
#str detect, only rows are the zip not meet sheets for the mpn
#r filter string multiple key words
#tidyverse left join
```

#adding the column with the zip not met sheet to og dataframe with folder and file 
```{r}
attachment_c_filenames = attachment_c_filenames %>% 
  left_join(zipnotmet_sheet, 
          by = c("folder" = "mpn"))

```

#Sheet names
#ZIPSnotmet, Zipsnotmet, Not Met Zips, Zips Not Met, C-5-ZipsNotmet, C5 - Not Met Zips, C5 Not Met Zips, ZipCodes Not Met, ZipCodesNotMet
```{r}
df_identify %>% 
  count(identify_sheets) %>% 
  arrange(desc(n)) %>% 
  merced.clc::dt_table(search = F,
                       row_nums = T)
```


#use for loop, pull sheet names, filter for sheets that have zips and not and met as a substring ; count sheet names to find most common one


#ZIPSnotmet, Zipsnotmet, Not Met Zips, Zips Not Met, C-5-ZipsNotmet, C5 - Not Met Zips, C5 Not Met Zips, ZipCodes Not Met, ZipCodesNotMet
```





















