---
title: "mpn_exploration_notebook"
format: html
---

Listing all the folders, recursive shows empty subfolder name
```{r}
list.dirs(path = here::here("data"), 
          full.names = FALSE,
          recursive = TRUE)

```

Tracking down empty subfolder name
```{r}

for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfolder = list.dirs(path = x, 
          full.names = FALSE,
          recursive = FALSE)


  if(length(subfolder) > 0) {print(x)}
  
}

```

```{r}
x= here::here("data/MPN 0060/")

subfolder = list.dirs(path = x, 
          full.names = FALSE,
          recursive = FALSE)

if(length(subfolder) > 0) {print(x)}
```

Listing files within mpn 0060 folder
```{r}
list.files(path = here::here("data/MPN 0060"))
```

run a for loop through the folders to pull all files and put into one character vector (df_files).
```{r}
df_files = c()
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = list.files(path = x, 
          full.names = FALSE,
          recursive = FALSE)
  df_files = c(df_files, subfiles)
  
}

```

Install and Load packages
```{r}
install.packages("stringr")
install.packages("tidyverse")
library(stringr)
library(tidyverse)
```

Detect files with 'geo'- (lower case 'g' was not working); and create a character vector with these files
```{r}
df_files = str_to_lower(df_files, locale = "en")
str_detect(df_files, "geo")
str_count(df_files, pattern = "geo")
geocoding_files <- str_subset(df_files, pattern = "geo", negate = FALSE)
```


create table describing folders
```{r}
df_files = tribble(~folder, 
                   ~num_geo_files,
                   ~num_pdf_files,
                   ~num_excel_files)
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = str_to_lower(list.files(path = x,
                                     full.names = FALSE,
                                     recursive = FALSE),
                          locale = "en")
  num_geo = sum(str_detect(subfiles, "geo"))
  
  num_pdf = sum(str_detect(subfiles,"pdf"))
  
  num_excel = sum(str_detect(subfiles, "xlsx|xls"))
  
  df_files = df_files %>%
    add_row(folder = basename(x),
            num_geo_files = num_geo,
            num_pdf_files = num_pdf,
            num_excel_files = num_excel)
  
}

```

adding column with list of geo file names
```{r}
df_files = tribble(~folder, 
                   ~num_geo_files,
                   ~num_pdf_files,
                   ~num_excel_files,
                   ~list_geo_files)
for (x in list.dirs(path = here::here("data/"), 
          full.names = TRUE,
          recursive = FALSE)) {
  
  subfiles = str_to_lower(list.files(path = x,
                                     full.names = FALSE,
                                     recursive = FALSE),
                          locale = "en")
  num_geo = sum(str_detect(subfiles, "geo"))
  
  geo_files = paste(str_subset(subfiles, 
                         pattern = "geo", 
                         negate = FALSE),
                    collapse = "; ")
  
  num_pdf = sum(str_detect(subfiles,"pdf"))
  
  num_excel = sum(str_detect(subfiles, "xlsx|xls"))
  
  df_files = df_files %>%
    add_row(folder = basename(x),
            num_geo_files = num_geo,
            num_pdf_files = num_pdf,
            num_excel_files = num_excel,
            list_geo_files = geo_files)
  
}

```


```{r}

df_files %>% 
  filter(num_geo_files>1)

```


create code that gets the correct excel file with data and input new column with the geo file we will work with 


files that are geo and xlsx files; # of pdfs that arent data; create a column- each row contains list of name of geo files